Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-14 paper/supplemental/architecture.tex
Update supplemental.

@@

We create a dense automatic segmentation of electron microscopy data using a combination of a U-net~\cite{RonnebergerFB15} and the GALA agglomeration method~\cite{nunez2014graph}. These classifiers are trained on different data than GP (Tab.~\ref{tab:trainingdata}).

@@

GALA uses a random forest classifier to agglomerate segments. We use an agglomeration level of 0.3 (after a grid search). Further details of our pipeline are described in~\cite{rhoananet}.

>>>>

We provide pseudo code on how we detect merge errors to foster understanding of the reported algorithm (Alg.~\ref{code:mergeerror}). In our experiments, we use $N=50$ iterations.

@@

We create a dense automatic segmentation of electron microscopy data using a combination of a U-net~\cite{RonnebergerFB15} and the GALA agglomeration method~\cite{nunez2014graph}. To not bias, these classifiers are trained on different data than GP (Tab.~\ref{tab:trainingdata}).

@@

GALA uses a random forest classifier to agglomerate segments. We use an agglomeration level of 0.3 (after a grid search). We follow the method by Knowles-Barley~\etal as described in~\cite{rhoananet}.
